---
title: "403A Project3 I(a)(b)(c)"
author: "Yining Qian"
date: "2017/12/4"
output: pdf_document
---
# Problem 1
```{r}
attach(healthcare.data)
```
(a) In this section, we firstly load the data from the website and find there are some missing data inside, so we use the function of "complete cases" to list all the rows of data that DONT have missing values.   
```{r}
library(readxl)
healthcare.data<-read.csv("C:/Users/lenovo/Desktop/german_healthcare_usage.csv")
healthcare.data<- healthcare.data[complete.cases(healthcare.data),]
```
Next, we are going to plot a histogram of different quantitiative variables. 
They are "AGE","ALC","HANDPER","EDUC","DOCVIS","HOSPVIS","NUMOBS""HSAT""LOGINC""HHNINC""NEWHSAT""PRESCRIP".  
(1)plot a histogram of variable "age"
```{r}
library(fitdistrplus)
hist(healthcare.data$AGE,main="Histogram of Age ",col=8,ylim=c(0,0.03),prob=TRUE)
lines(density(healthcare.data$AGE),ylab="Frequency",col="red",lwd=2)
legend('topright',c("Histogram","Density"),fill=c("8","red"))
descdist(healthcare.data$AGE,boot=1000)
```

As we can see from the Cullen and Frey graph above, the variable "AGE" fits a uniform distribution because the "observation"(blue circile) perfectly covers the "triangle"(Uniform Distribution).  

(2)Plot a histogram of variable "ALC"
```{r}
hist(healthcare.data$ALC,main="Histogram of ALC ",col=8,ylim=c(0,0.03),prob=TRUE)
lines(density(healthcare.data$ALC),ylab="Frequency",col="red",lwd=2)
legend('topright',c("Histogram","Density"),fill=c("8","red"))
descdist(healthcare.data$ALC,boot=1000)
```
As we can see from the Cullen and Frey graph above, the variable "ALC" fits a uniform distribution because the "observation"(blue circile) perfectly covers the "triangle"(Uniform Distribution)

(3)Plot a histogram of variable "LOGINC"
```{r}
hist(healthcare.data$LOGINC,col=8,ylim=c(0,1.1),main="Histogram of LOGINC ",prob=TRUE)
lines(density(healthcare.data$LOGINC),ylab="Frequency",col="red",lwd=2)
legend('topright',c("Histogram","Density"),fill=c("8","red"))
descdist(healthcare.data$LOGINC,boot=1000)
```
As we can see from the graph above, it is not easy to decide between "norm" and "logistic" distribution.So next, we are going to verify whether it is "norm" or "logistic".
```{r}
fit_loginc1<-fitdist(healthcare.data$LOGINC,"norm")
fit_loginc2<-fitdist(healthcare.data$LOGINC,"logis")
plot(fit_loginc1)
plot(fit_loginc2)
cdfcomp(list(fit_loginc1,fit_loginc2))
par(mfrow=c(2,2))
plot.legend<-c("normal","logis")
cdfcomp(list(fit_loginc1,fit_loginc2),legendtext=c("normal","logistic"))
denscomp(list(fit_loginc1,fit_loginc2),legendtext=c("normal","logistic"))
qqcomp(list(fit_loginc1,fit_loginc2),legendtext=c("normal","logistic"))
ppcomp(list(fit_loginc1,fit_loginc2),legendtext=c("normal","logistic"))
gofstat(list(fit_loginc1,fit_loginc2),fitnames=c("normal","logistic"))
```

As we can see from the results above, "LOGINC" fits normal distribution better. 

(4)Plot a histogram of variable "HHNINC"
```{r}
hist(healthcare.data$HHNINC,col=8,ylim=c(0,1.1),main="Histogram of HHNINC ",prob=TRUE)
lines(density(healthcare.data$HHNINC),ylab="Frequency",col="red",lwd=2)
legend('topright',c("Histogram","Density"),fill=c("8","red"))
descdist(healthcare.data$HHNINC,boot=1000)
```

As we can see from the results above, it's hard to define which distribution we could fit. Therefore, we need to verify whether it is "gamma" or "lognormal".
```{r}
fit_hhninc1<-fitdist(healthcare.data$HHNINC,"gamma")
fit_hhninc2<-fitdist(healthcare.data$HHNINC,"lnorm")
plot(fit_hhninc1)
plot(fit_hhninc2)
cdfcomp(list(fit_hhninc1,fit_hhninc2))
par(mfrow=c(2,2))
plot.legend<-c("gamma","lognormal")
cdfcomp(list(fit_hhninc1,fit_hhninc2),legendtext=c("gamma","lognormal"))
denscomp(list(fit_hhninc1,fit_hhninc2),legendtext=c("gamma","lognormal"))
qqcomp(list(fit_hhninc1,fit_hhninc2),legendtext=c("gamma","lognormal"))
ppcomp(list(fit_hhninc1,fit_hhninc2),legendtext=c("gamma","lognormal"))
gofstat(list(fit_hhninc1,fit_hhninc2),fitnames=c("gamma","lognormal"))
```
From the results above, "HHNINC" fits gamma distribution better.  

(5)Plot a histogram of variable "EDUC"
```{r}
hist(healthcare.data$EDUC,col=8,ylim=c(0,1.1),main="Histogram of EDUC",prob=TRUE)
lines(density(healthcare.data$EDUC),ylab="Frequency",col="red",lwd=2)
legend('topright',c("Histogram","Density"),fill=c("8","red"))
descdist(healthcare.data$EDUC,boot=1000)
```
As we can see from the results above, it's hard to define which distribution we could fit. Therefore, we need to verify whether it is "beta" or "lognormal".  
```{r}
fit_educ1<-fitdist(healthcare.data$EDUC,"gamma")
fit_educ2<-fitdist(healthcare.data$EDUC,"lnorm")
plot(fit_educ1)
plot(fit_educ2)
cdfcomp(list(fit_educ1,fit_educ2))
par(mfrow=c(2,2))
plot.legend<-c("gamma","lognormal")
cdfcomp(list(fit_educ1,fit_educ2),legendtext=c("gamma","lognormal"))
denscomp(list(fit_educ1,fit_educ2),legendtext=c("gamma","lognormal"))
qqcomp(list(fit_educ1,fit_educ2),legendtext=c("gamma","lognormal"))
ppcomp(list(fit_educ1,fit_educ2),legendtext=c("gamma","lognormal"))
gofstat(list(fit_educ1,fit_educ2),fitnames=c("gamma","lognormal"))
```
From the results above, "EDUC" fits lognormal distribution better.  
(6)Plot a histogram of variable "DOCVIS"
```{r}
hist(healthcare.data$DOCVIS,col=8,ylim=c(0,1.1),main="Histogram of DOCVIS",prob=TRUE)
lines(density(healthcare.data$DOCVIS),ylab="Frequency",col="red",lwd=2)
legend('topright',c("Histogram","Density"),fill=c("8","red"))
descdist(healthcare.data$DOCVIS,boot=1000)
```
From the results above, "DOCVIS" fits lognormal distribution better.  
(7)Plot a histogram of variable "HOSPVIS"
```{r}
hist(healthcare.data$HOSPVIS,col=8,ylim=c(0,1.1),main="Histogram of HOSPVIS",prob=TRUE)
lines(density(healthcare.data$HOSPVIS),ylab="Frequency",col="red",lwd=2)
legend('topright',c("Histogram","Density"),fill=c("8","red"))
descdist(healthcare.data$HOSPVIS,boot=1000)
```
From the results above, "HOSPVIS" fits beta distribution better.  
(8)Plot a histogram of variable "NUMOBS"
```{r}
hist(healthcare.data$NUMOBS,col=8,ylim=c(0,1.1),main="Histogram of NUMOBS",prob=TRUE)
lines(density(healthcare.data$NUMOBS),ylab="Frequency",col="red",lwd=2)
legend('topright',c("Histogram","Density"),fill=c("8","red"))
descdist(healthcare.data$NUMOBS,boot=1000)
```
As we can see from the results above, it's hard to define which distribution we could fit. Therefore, we need to verify whether it is "uniform" ,"gamma" or "normal". 
```{r}
fit_numobs1<-fitdist(healthcare.data$NUMOBS,"unif")
fit_numobs2<-fitdist(healthcare.data$NUMOBS,"norm")
fit_numobs3<-fitdist(healthcare.data$NUMOBS,"gamma")
plot(fit_numobs1)
plot(fit_numobs2)
plot(fit_numobs3)
cdfcomp(list(fit_numobs1,fit_numobs2,fit_numobs3))
par(mfrow=c(3,3))
plot.legend<-c("uniform","norm","gamma")
cdfcomp(list(fit_numobs1,fit_numobs2,fit_numobs3),legendtext=c("uniform","normal","gamma"))
denscomp(list(fit_numobs1,fit_numobs2,fit_numobs3),legendtext=c("uniform","normal","gamma"))
qqcomp(list(fit_numobs1,fit_numobs2,fit_numobs3),legendtext=c("uniform","normal","gamma"))
ppcomp(list(fit_numobs1,fit_numobs2,fit_numobs3),legendtext=c("uniform","normal","gamma"))
gofstat(list(fit_numobs1,fit_numobs2,fit_numobs3),fitnames=c("uniform","normal","gamma"))
```
From the results above, "NUMOBS" fits lognormal distribution better.  
(9)Plot a histogram of variable "HANDPER"
```{r}
hist(healthcare.data$HANDPER,col=8,ylim=c(0,1.1),main="Histogram of HANDPER",prob=TRUE)
lines(density(healthcare.data$HANDPER),ylab="Frequency",col="red",lwd=2)
legend('topright',c("Histogram","Density"),fill=c("8","red"))
descdist(healthcare.data$HANDPER,boot=1000)
```
From the results above, "HANDPER" fits gamma distribution better.  
(10)Plot a histogram of variable "NEWHSAT"
```{r}
hist(healthcare.data$NEWHSAT,col=8,ylim=c(0,1.1),main="Histogram of NEWHSAT",prob=TRUE)
lines(density(healthcare.data$NEWHSAT),ylab="Frequency",col="red",lwd=2)
legend('topright',c("Histogram","Density"),fill=c("8","red"))
descdist(healthcare.data$NEWHSAT,boot=1000)
```
From the results above, "HSAT" fits normal distribution better. 

(11)Plot a histogram of variable "PRESCRIP"
```{r}
hist(healthcare.data$PRESCRIP,col=8,ylim=c(0,1.1),main="Histogram of PRESCRIP",prob=TRUE)
lines(density(healthcare.data$PRESCRIP),ylab="Frequency",col="red",lwd=2)
legend('topright',c("Histogram","Density"),fill=c("8","red"))
descdist(healthcare.data$PRESCRIP,boot=1000)
```
From the results above, "HSAT" fits lognormal distribution better.  

(b) barplot
(1)barplot of variable "FEMALE"
```{r}
## Simple bar plot
counts<-table(FEMALE)
barplot(counts,main="Female",xlab="Gender Condition",col=c("0","8"),ylim=c(0,18000))

## Add a legend
legend('topright',c("Male","Female"),fill=c("0","8"))
```
(2)barplot of variable "YEAR"
```{r}
## Simple bar plot
counts<-table(YEAR)
barplot(counts,main="Year",xlab="Year",col=c("0","1","2","3","4","8"))

## Add a legend
legend('topright',c("YEAR"),fill=c("0","8"))
```
(3)barplot of variable "HANDDUM"
```{r}
## Simple bar plot
counts<-table(HANDDUM)
barplot(counts,main="HANDDUM",xlab="HANDDUM condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","handicapped"),fill=c("0","8"))
```
(4)barplot of variable "HHKIDS"
```{r}
## Simple bar plot
counts<-table(HHKIDS)
barplot(counts,main="HHKIDS",xlab="Children under 16 in the household condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Children under 16"),fill=c("0","8"))
```
(5)barplot of variable "MARRIED"
```{r}
## Simple bar plot
counts<-table(MARRIED) 
barplot(counts,main="MARRIED",xlab="Married condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Married"),fill=c("0","8"))
```

(6)barplot of variable "HAUPTS"
```{r}
## Simple bar plot
counts<-table(HAUPTS)
barplot(counts,main="HAUPTS",xlab="Highest Schooling degree is Hauptschul Degree condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Highest Schooling degree is Hauptschul Degree"),fill=c("0","8"))
```

(7)barplot of variable "REALS"
```{r}
## Simple bar plot
counts<-table(REALS)
barplot(counts,main="REALS",xlab="Highest Schooling degree is Realschul Degree condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Highest Schooling degree is Realschul Degree"),fill=c("0","8"))
```

(8)barplot of variable "FACHHS"
```{r}
## Simple bar plot
counts<-table(FACHHS)
barplot(counts,main="FACHHS",xlab="Highest Schooling degree is Polytechnical Degree condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Highest Schooling degree is Polytechnical Degree"),fill=c("0","8"))
```

(9)barplot of variable "ABITUR"
```{r}
## Simple bar plot
counts<-table(ABITUR)
barplot(counts,main="ABITUR",xlab="Highest Schooling degree is ABITUR condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Highest Schooling degree is ABITUR"),fill=c("0","8"))
```

(10)barplot of variable "UNIV"
```{r}
## Simple bar plot
counts<-table(UNIV)
barplot(counts,main="UNIV",xlab="Highest Schooling degree is University Degree condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Highest Schooling degree is University Degree"),fill=c("0","8"))
```

(11)barplot of variable "WORKING"
```{r}
## Simple bar plot
counts<-table(WORKING)
barplot(counts,main="WORKING",xlab="Working condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Working"),fill=c("0","8"))
```

(12)barplot of variable "BLUEC"
```{r}
## Simple bar plot
counts<-table(BLUEC)
barplot(counts,main="BLUEC",xlab="Blue Collar Employee condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Blue Collar Employee"),fill=c("0","8"))
```

(13)barplot of variable "WHITEC"
```{r}
## Simple bar plot
counts<-table(WHITEC)
barplot(counts,main="WHITEC",xlab="White Collar Employee condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","White Collar Employee"),fill=c("0","8"))
```

(14)barplot of variable "SELF"
```{r}
## Simple bar plot
counts<-table(SELF)
barplot(counts,main="SELF",xlab="Self Employed condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Self Employed"),fill=c("0","8"))
```

(15)barplot of variable "BEAMT"
```{r}
## Simple bar plot
counts<-table(BEAMT)
barplot(counts,main="BEAMT",xlab="Civil servant condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Civil Servant"),fill=c("0","8"))
```

(16)barplot of variable "UNEMPLOY"
```{r}
## Simple bar plot
counts<-table(UNEMPLOY)
barplot(counts,main="UNEMPLOY",xlab="Umemployed condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Umemployed"),fill=c("0","8"))
```

(17)barplot of variable "HSAT"
```{r}
## Simple bar plot
counts<-table(HSAT)
barplot(counts,main="HSAT",xlab="Health Satisfaction condition",col=c("0","1","2","3","4","5","6","7","8","9","10"))

## Add a legend
legend('topright',c("Health Satisfaction"),fill=c("0","8"))
```

(18)barplot of variable "DOCTOR"
```{r}
## Simple bar plot
counts<-table(DOCTOR)
barplot(counts,main="DOCTOR",xlab="Dummy Variable",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","DOCVIS > 0"),fill=c("0","8"))
```

(19)barplot of variable "HOSPITAL"
```{r}
## Simple bar plot
counts<-table(HOSPITAL)
barplot(counts,main="HOSPITAL",xlab="Dummy Variable",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","HOSPVIS > 0"),fill=c("0","8"))
```

(20)barplot of variable "HEALTHY"
```{r}
## Simple bar plot
counts<-table(HEALTHY)
barplot(counts,main="HEALTHY",xlab="Healthy condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Healthy"),fill=c("0","8"))
```

(21)barplot of variable "PUBLIC"
```{r}
## Simple bar plot
counts<-table(PUBLIC)
barplot(counts,main="PUBLIC",xlab="Insured condition in public health insurance",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Insured in public health insurance"),fill=c("0","8"))
```

(22)barplot of variable "ADDON"
```{r}
## Simple bar plot
counts<-table(ADDON)
barplot(counts,main="ADDON",xlab= "add-on insurance condition",col=c("0","8"))

## Add a legend
legend('topright',c("Otherwise","Insured by add-on insurance"),fill=c("0","8"))
```

(c)Linear Regression Model
```{r}
##Conduct linear regression model that includes all the varibales
LRM <- lm(DOCVIS~ID+FEMALE+YEAR+AGE+HANDDUM+ALC+FAMHIST+HANDPER+HHKIDS+EDUC+MARRIED+HAUPTS+REALS+FACHHS+ABITUR+UNIV+WORKING+BLUEC+WHITEC+SELF+BEAMT+HOSPVIS+UNEMPLOY+PUBLIC+ADDON+NUMOBS+DOCTOR+HEALTHY+YEAR1984+YEAR1985+YEAR1986+YEAR1987+YEAR1988+YEAR1991+YEAR1994+LOGINC+HOSPITAL+HHNINC+NEWHSAT+PRESCRIP)
summary(LRM)
```

